Project Plan for a Time Series Visualization Framework

### 2016-04-28 docs/projectplan/projectplan.tex
added description for some visualization primitives for the projectplan

In today's society data plays a import role in many different ways.
For instance, businesses are using large amount of data to predict consumer behavior to satisfy their demand.
Often time plays a essential role in these data sets. 
For example, the consumption of electricity does not only depend on the time of the day but also on the day of the week and other seasonal effects.
Such data sets are usually referred to as time series (i.e. two- or higher-dimensional data with time as one dimension).

@@

Another important part of the back-end is the visualization engine. 
Its main responsibility is the processing of the time series to create visualization primitives (i.e. it transforms the data into a representation that can later be rendered by the front-end).
The visualization engine provides a RESTful API for its functionality, which is another part of the back-end.
This allows the front-end to send simple HTTP requests to get visualizations of the time series.

>>>>

In today's society data plays a import role in many different ways.
For instance, businesses are using large amount of data to predict consumer behavior to satisfy their demand.
Often time plays a essential role in these data sets. 
For example, the consumption of electricity does not only depend on the time of the day, but also on the day of the week and other seasonal effects.
Such data sets are usually referred to as time series (i.e. two- or higher-dimensional data with time as one dimension).

@@

Another important part of the back-end is the visualization engine. 
Its main responsibility is the processing of the time series to create visualization primitives (i.e. it transforms the data into a representation that can later be rendered by the front-end).
The visualization engine provides a RESTful API for its functionality, which is another part of the back-end.
This allows the front-end to send simple HTTP requests to get visualization primitives of the time series.
To implement the API we'll use the Flask microframework which makes things like RESTful request dispatching quite easy.

The front-end of the application is a simple HTML5 website that uses a JavaScript visualization library to display the visualization primitives.
Which JavaScript visualization library will be used was not decided yet.
However, a little bit of research showed that there plenty of different libraries available which support the plotting of temporal data.
For example, two time series visualization libraries that are based on the well-known D3.js libary are Cubism.js and MetricsGraphics.js could be used for this project.
Currently we plan to support the following visualization primitives which can be generated by the visualization engine and can be requested by the front-end:

\begin{enumerate}
 \item Simple time series graphs, which plot the observations (i.e. the data points) against the time of the observations.
 \item Filters for the time series graphs, which allow the user to select only data in a certain time span.
 \item Possibility to show multiple time series in the same figure or in linked figures.
 \item Possibility to show the running average and running standard deviation of a time series (used to determine stationarity of a time series).
 \item Time series graphs which are live updated whenever new data is available on a socket (i.e. live visualization of a time series).
 \item Seasonal plots (i.e. plots where the data is plotted against the individual season in which it was observed).
 \item Autocorrelation function (ACF) plots, which are a statistical tool to proof seasonal effects in the data.
\end{enumerate}

% TODO: visual evaluation of a model
